FoRTE Disturbance Paper Analysis

### 2021-05-10 C.analysis/paper_analysis.Rmd
Adding met analysis

```{r}
ggplot(data = disturbance) + 
  geom_line(aes(year, value, color = severity, line = met), alpha = 0.5) + 
  facet_wrap("variable", scales = 'free') +
  THEME +
  labs(y = "ln(treatment/control)") +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  labs(title = "Disturbance Response")
```

>>>>

```{r}
disturbance %>%  
  mutate(Severity = severity) %>% 
  ggplot() + 
  geom_line(aes(year, value, color = Severity, line = met), alpha = 0.5) + 
  facet_wrap("variable", scales = 'free') +
  THEME +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  labs(y = "ln(treatment/control)", x = "Year") 
```
